Ktirio Urban Building: A Computational Framework for City Energy Simulations Enhanced by CI/CD Innovations on EuroHPC Systems

### 2024-11-06 article.hid2-ub-cicd.ppam24.tex
Updates from Overleaf

\documentclass[runningheads]{llncs}
\usepackage{fullpage}
\usepackage{graphicx} % for including images
\usepackage{float}
\usepackage[T1]{fontenc}
\usepackage{wrapfig}
\usepackage[]{subcaption}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{siunitx}
\usepackage{ragged2e}
\usepackage{multicol}
\usepackage{url}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage{paralist}
\usepackage{amsmath}
\definecolor{darkred}{rgb}{0.6, 0, 0}
\definecolor{darkgreen}{rgb}{0, 0.5, 0}
\definecolor{darkblue}{rgb}{0, 0, 0.5}
\definecolor{darkmagenta}{rgb}{0.5, 0, 0.5}
\usepackage{hyperref}

@@

Building on the foundations of the Feel++ framework, this paper introduces an innovative CI/CD environment specifically designed for deployment on EuroHPC JU supercomputers. 
This environment enhances our ability to develop and test simulations rapidly and provides a robust platform for deploying and running these simulations at multiple scales. 
By leveraging containerized environments, we ensure that all dependencies are encapsulated, making the simulations portable and reproducible across different supercomputing resources. 
These containers are deployed on EuroHPC JU infrastructures, which represents a significant advancement in making high-performance computing resources accessible for urban simulation studies. 
The use of containers also simplifies software management and ensures consistency in the deployment process, enabling seamless scalability and reliability across EuroHPC systems.

Thanks to synergies with other CoE HiDALGO2 pilots, the KUB project is set to integrate building simulations with Urban Air Pollution (UAP) pilot models to comprehensively assess the environmental impact of building stocks soon. This integration improves the predictive accuracy of the simulations by incorporating data such as wind speed and solar radiation, enhancing the models' responsiveness and forecasts to environmental conditions.

@@

We describe our definition of Levels of Detail for Buildings such as:
\begin{description}
    \item[LOD-0] The most straightforward form, representing buildings as oriented bounding boxes. This level is typically used for large-scale preliminary analyses and quick visual assessments.
    \item[LOD-1] Buildings are represented as polygonal extrusions, with added roof structures to improve the visual accuracy and utility in simulations that do not require detailed internal features.
    \item[LOD-2] At this level, buildings are detailed using Industry Foundation Classes (IFC) standards, supporting detailed thermal and structural analyses. This includes detailed geometries for each building entity, often using complex surface models like B-REP, swept solids, or CSG techniques.
\end{description}

\begin{figure}[ht]%{R}{1\textwidth} % 'R' or 'L' for right or left, and width
\centering
\subfloat[LOD-0: a building is represented by its bounding box]{%
  \includegraphics[width=0.45\linewidth]{img-compressed-buildings-lod0.png}
  \label{fig:building-lod0}
}\hspace{0.05\linewidth}
%\hfill % This ensures that the images are placed side by side
\subfloat[LOD-1: a building is represented by its ground footprint elevated to its height]{%
  \includegraphics[width=0.45\linewidth]{img-compressed-buildings-lod1.png}
  \label{fig:building-lod1}
}\\ % Ends the line for the first row of figures

\subfloat[LOD-2: a building in full detail using BIM. Note that LOD-2 and LOD-1 are mixed.]{%
  \includegraphics[width=0.45\linewidth]{img-compressed-buildings-lod2.png}
  \label{fig:building-lod2}
}\hspace{0.05\linewidth}
%\hfill
\subfloat[LOD-2: A zoom on the LOD-2 building.]{%
  \includegraphics[width=0.45\linewidth]{img-compressed-buildings-lod2-zoom.png}
  \label{fig:building-lod2-zoom}
}

\caption{Different representations of a building using our LOD definition}
\label{fig:buildings}

\end{figure}

In \cref{fig:buildings}, we illustrate the different levels of details. 
\Cref{fig:building-lod0} displays the LOD-0 of a building with its bounding box. 
\Cref{fig:building-lod1} displays the LOD-1 of a building using its footprint elevated to its height. 
\Cref{fig:building-lod2} and~\cref{fig:building-lod2-zoom} display the LOD-2 representation using BIM. 
In \Cref{fig:city-strasbourg}, we display an illustration of the center of the city of Strasbourg with LOD-0, see \cref{fig:city-strasbourg-lod0}, and LOD-1, see \cref{fig:city-strasbourg-lod1}, representations.

@@

\subsubsection{Terrain Modeling}
The terrain modeling process utilizes elevation data extracted from raster images. The initial step involves creating a uniform mesh based on the size of the raster image. Following this, the elevation at each node is evaluated.
However, this method provides a very refined mesh, even when the terrain is flat. For this reason, we plan to apply a mesh adaptation technique to reduce mesh density where feasible, using the following processing:
\begin{inparaenum}[\it (i)]
    \item Compute an arbitrary number of isolines for elevation,
    \item Build a new terrain mesh conform with the isolines nodes and adapt to terrain elevation gradient.
\end{inparaenum}
%Subsequently, isolines for elevation are computed, and mesh adaptation techniques are applied to reduce mesh density where feasible. Finally, each tile is glued together to ensure the continuity of the terrain mesh.

\subsubsection{Vegetation Modeling}

Including vegetation (trees) in our geometric model is essential for the simulation of buildings. The shading provided by trees and the cooling provided by wooded areas had a significant impacts on building environment  . We use the OpenStreetMap database to obtain the metadata associated with the vegetation. In addition to the position of the trees, we can also obtain other information, such as the tree's height and species. The current strategy is as follows:
\begin{inparaenum}[\it (i)]
\item Definition of a reference tree library that lists a certain number of tree species at different levels of precision (LOD). These geometric entities are parameterized so that a transformation can be applied.
\item Fetching vegetation metadata via OpenStreetMap. The attributes (height, species) are not always available, so we try to define them as best as we can (by searching around).
\item Creating a tree geometric model using an affine transformation of the reference tree model.
\end{inparaenum}

\subsubsection{Integration of all urban geometric components}

This process involves creating a conforming mesh that includes all components (buildings, terrains, vegetation). Moreover, this step requires accomplishing some challenges by using complex geometric algorithms to realize the following points: \textit{(i)} Ensure that buildings on slopes are accurately modeled by adapting their height and embedding them into the terrain mesh. 
\Cref{fig:city-grenoble-terrain} illustrates this aspect; \textit{(ii)} applies the intersection of buildings and consequently defines contact zones that can be included in building thermal models (coupling). \textit{(iii)} Apply the intersection of vegetation with buildings and terrain; and finally \textit{(iv)} Improve mesh quality after the previous geometric operations (mesh adaption).

@@

All the features described above are not yet operational in our framework. We can reconstruct a geometric model of an urban area whose location is arbitrary so that the user can select an area anywhere in the world. The final mesh comprises all buildings LOD-0 or LOD-1 and the terrain with elevation. The integration of all the urban components is currently being investigated. This part requires fairly costly algorithms (mesh intersection), for which it will be necessary to form groups intelligently to reduce the computational cost.

\paragraph{Current Mesh Generation Strategy}
The current strategy for mesh generation employs multi-threading (MT) to handle various stages of the mesh construction process. Initially, the tiles used are determined based on the specified location, a task performed sequentially. Following this, GIS data, including buildings and elevation information, is downloaded in parallel. Next, polygons are repaired~\cite{loriot_polygon_2024} to ensure they are suitable for mesh generation, with this process executed in parallel using MT. The terrain mesh is then generated in parallel, employing CGAL's algorithms to ensure precision and efficiency. Union operations at tile junctions are performed to ensure continuity, a step that is currently sequential. Finally, building meshes are generated using a parallel MT approach, leveraging CGAL for its advanced mesh generation capabilities.

@@

Data partitioning is a crucial stage in the deployment of the supercomputer simulator. We need to partition the geometry of the city in such a way as to distribute the simulation computation correctly.
Different partitioning strategies are considered depending on the specific requirements of the simulation use cases :
\begin{inparadesc}
\item[Case 0] simulate simple scenarios where buildings do not interact with their environment, a basic listing and weighting strategy is sufficient;
\item[Case 1] simulate buildings interact with environmental elements, a more complex partitioning strategy is necessary that considers both the buildings and their immediate non-building surroundings; the build meshes and environment meshes (terrain, vegetation) are integrated conformably; each component can be partitioned separately;
\item[Case 2] simulate full interaction models where the partitioning strategy starts with the buildings and extends to the entire urban mesh, ensuring all elements are considered to minimize communication overhead;
\item[Case 3] simulate scenarios with extreme partitioning and employ a multi-grid approach to  define coarse and fine meshes and manage computational resources efficiently; this multi-fidelity approach enhances the accuracy and applicability of urban models in simulations and ensures scalability across different computational platforms, making it a cornerstone of urban analysis.
\end{inparadesc}

The current version of our simulation framework has implemented case 0 and case 1. Cases 2 and 3 require a full conformal mesh, which is not yet available. Moreover, these partitioning strategies are costly, so we have planned to use other third-party tools, such as Zoltan2~\cite{the_zoltan2_team_zoltan2_nodate}, to improve efficiency.
\begin{wrapfigure}{R}{0.7\textwidth}
\centering
\subfloat[Partitioning Case 0\label{fig:city-strasbourg-lod0-parts}]{%
  \includegraphics[width=0.46\linewidth]{img-compressed-city-strasbourg-lod0-parts.png}
}\hspace{0.02\linewidth}
%\hfill % Ensures that the images are placed side by side
\subfloat[Partitioning Case 1\label{fig:city-strasbourg-lod1-parts}]{%
  \includegraphics[width=0.46\linewidth]{img-compressed-city-strasbourg-lod1-parts.png}
}
%\subfloat[Partitioning Case 3: Large scale\label{fig:city-ny-largescale}]{%
%  \includegraphics[width=0.4\textwidth]{img-compressed-city-newyork-largescale.png}
%}
\caption{Mesh partitioning illustrations}
\label{fig:partitioning}
\end{wrapfigure}

\Cref{fig:partitioning} illustrates the different strategies discussed previously and presents a reconstruction of New York City in \cref{fig:city-ny-largescale}. This geometric model has an area of 400 $km^2$ (20 km square side of 20 km) and has generated around 450000 buildings. This example requires the large-scale approach discussed but not yet implemented or tested.

@@

\subsubsection{Heat transfer model in buildings}
\label{sec:heat-transfer-in-buildings}

The physical model of city buildings is currently based on a multizone model.
One zone is allocated per building floor. 
The energy balance for each zone is calculated by taking into account energy exchanges with adjacent zones and the environment.

The energy balance is written according to the first law of thermodynamics: in an isolated system, the sum of all forms of energy is constant.

\begin{equation}
    C \frac{dT}{dt} = \phi_{\mathrm{HVAC}} + \phi_{\mathrm{gain}} - \phi_{\mathrm{losses}}
\end{equation}
where
\begin{inparaenum}[\it (i)]
    \item $C \dfrac{dT}{dt}$ represents the thermal inertia of the construction, quantifying how the temperature of the zone changes over time due to its thermal mass. Specifically,
    $C$ is a measure of how much heat a material can store and release, combining the heat capacity of the construction (how much energy is required to change the temperature) with the rate of temperature change and 
    $\dfrac{dT}{dt}$ is the rate of change of temperature with respect to time. A higher thermal inertia means the construction will have a slower rate of temperature change in response to energy inputs and losses, effectively buffering temperature fluctuations;
    \item $\phi_{\mathrm{HVAC}}$ represents the energy input from the Heating, Ventilation, and Air Conditioning (HVAC) systems. It includes energy added to the zone to maintain desired temperature levels;
    \item $\phi_{\mathrm{gain}}$, referred to as free energy gain, includes solar gains (heat from sunlight) and internal gains (heat generated by occupants and equipment);
    \item $\phi_{\mathrm{losses}}$ represents the energy lost through walls, roofs, floors, and air exchanges with the environment.
\end{inparaenum}

\begin{description}
  \item[HVAC heat flow] In the version of the model at the time of writing, the HVAC system is treated as an ideal heat source, which means it adjusts its output to maintain a set temperature within the building.
  \item[Heat gain] Heat gain is the addition of energy to the building, derived from two sources: \textbf{internal heat gains} and \textbf{solar heat gains}.
  \item[Internal heat gain] The internal heat gain captures the heat produced by occupants inside the building. 
  It is modeled as a function of metabolic rate $\mathrm{Met}$ and the number of inhabitants, $d_i$, which varies over time $t$:
  \begin{equation}
    \phi_{\mathrm{int}} = \mathrm{Met} \cdot d_i(t)
  \end{equation}

\item[Solar heat gain] The total solar heat gain includes contributions from direct, diffuse, and reflected solar radiation, taking into account the building’s surface characteristics and shading coefficient:
\begin{equation}
  \phi_{\mathrm{solar}} = \alpha \cdot S \cdot \left( E_{\mathrm{dir}} + E_{\mathrm{diff}} + E_{\mathrm{ref}} \right) \cdot S_C
\end{equation}
Direct solar radiation is the component of solar radiation adjusted for the angle of incidence of the sunlight:
\begin{equation}
  E_{\mathrm{dir}} = F_{\mathrm{dir}} \cdot \cos(I)
\end{equation}
Here, $F_{\mathrm{dir}}$ is the direct solar radiation, which is a function of the horizontal solar radiation measured by a weather station:
\begin{equation}
  F_{\mathrm{dir}} = \dfrac{F_{\mathrm{dir,Hz}}}{\sin(H_s)}
\end{equation}
The term $\cos(I)$ calculates the cosine of the angle of incidence of sunlight, incorporating the sun's altitude and azimuth angles as well as the building's tilt angle:
\begin{equation}
  \cos(I) = \cos(H_s) \cdot \sin(\beta) \cdot \cos(A_{zs} - A_z) + \sin(H_s) \cdot \cos(\beta)
\end{equation}
Diffuse solar radiation includes contributions from the sky dome and is adjusted for the building's tilt:
\begin{equation}
  E_{\mathrm{diff}} = F_{\mathrm{dif,Hz}} \cdot \left( \dfrac{1 + \cos(\beta)}{2} \right)
\end{equation}
Reflected solar radiation is calculated using the total horizontal radiation and the environment's albedo:
\begin{equation}
  E_{\mathrm{ref}} = \left[ F_{\mathrm{dir,Hz}} + F_{\mathrm{dif,Hz}} \right] \cdot \left( \dfrac{1 + \cos(\beta)}{2} \right) \cdot \text{albedo}
\end{equation}

\item[Conduction losses] Energy loss through walls is computed by summing the losses across all wall segments. It depends on the heat transfer coefficient, the wall area, and the temperature difference between the indoor and outdoor environments. In our current model, we simplify the calculations by not including the effects of thermal bridges, as they depend on specific information about the building's envelope, which we do not have:
\begin{equation}
  \phi_{\mathrm{wall}} = \sum_{j} U_j \cdot S_j \cdot \Delta T
\end{equation}
The convection losses are computed differently depending on the surface of the wall to which they are applied. On the interior surface, we apply a constant:
\begin{equation}
  \phi_{\mathrm{conv,int}} = \alpha_{\mathrm{conv}} \cdot \Delta T
\end{equation}
On the exterior surface, we use a forced convection model:
\begin{equation}
  \phi_{\mathrm{conv,ext}} = \left( 1.8 + 4.8 \cdot v_{\mathrm{air}} \right) \cdot \Delta T
\end{equation}

\item[Radiation losses] Radiation losses describe the heat energy lost due to thermal radiation, impacting both energy efficiency and thermal comfort.
We differentiate between the exterior of the wall that exchanges with the sky and the interior where the walls exchange with each other.
namely, for the exterior radiation exchange:
\begin{equation}
  \phi_{\mathrm{net,sky}} = \varepsilon_i \cdot \sigma \cdot \left( T_i^4 - T_{\mathrm{sky}}^4 \right)
\end{equation}
and for the interior radiation exchange:
\begin{equation}
  J[i] = \varepsilon_i \cdot \sigma \cdot T_i^4 + \left( 1.0 - \varepsilon_i \right) \cdot \sum_{j=1}^{n} F[i,j] \cdot J[j]
\end{equation}
where the radiative heat exchange $J[i]$ includes two terms:
\begin{inparaenum}[\it (i)]
    \item $\varepsilon_i \cdot \sigma \cdot T_i^4$, which calculates the heat radiated by surface $i$ where $\varepsilon_i$ measures how effectively the surface emits radiation and $T_i^4$ reflects that radiative heat loss increases rapidly with temperature; and
    \item $\left( 1.0 - \varepsilon_i \right) \cdot \sum_{j=1}^{n} F[i,j] \cdot J[j]$, which accounts for the heat absorbed from other surfaces $j$ within the zone. The factor $\left( 1.0 - \varepsilon_i \right)$ adjusts for the fraction of incoming radiation not emitted by surface $i$.
\end{inparaenum}
The net radiation flow is given by:
\begin{equation}
  \phi_{\mathrm{net,int}}[i] = S \cdot \dfrac{\varepsilon_i}{1.0 - \varepsilon_i} \cdot \left( \sigma \cdot T_i^4 - J[i] \right)
\end{equation}
Net radiation flow $Q_{\mathrm{flow}}[i]$ considers:
\begin{inparaenum}[\it (i)]
    \item $\dfrac{\varepsilon_i}{1.0 - \varepsilon_i} \cdot \left( \sigma \cdot T_i^4 - J[i] \right)$, which calculates the net heat flow due to radiation for surface $i$, considering the difference between the heat emitted by the surface and the heat received from other surfaces. The ratio $\dfrac{\varepsilon_i}{1.0 - \varepsilon_i}$ scales the net flow based on the emissivity of the surface.
\end{inparaenum}

\item[Air change] This term represents the energy loss due to air exchange between the zone and the exterior:
\begin{equation}
  \phi_{\mathrm{air}} = 0.34 \cdot Q_v \cdot \Delta T
\end{equation}
\end{description}
The described thermal models are implemented using the Modelica language, which is an object-oriented, equation-based language well-suited for modeling complex physical systems. 
These models are then transformed into Functional Mock-up Units (FMUs) compliant with the Functional Mock-up Interface (FMI) standard. 
FMUs encapsulate the models and enable them to be shared and integrated across different simulation environments.

\paragraph{Conclusion} By integrating these models within a high-performance computing framework, it is possible to simulate the thermal behavior of city-scale building clusters.
This facilitates the assessment of energy consumption, thermal comfort, and the impact of various energy-saving strategies under different environmental conditions and operational scenarios.

@@

\paragraph{Numerical Methods and Challenges}
Both shading masks and view factors are computed using Monte Carlo and ray tracing techniques, which allow for handling complex geometries with various obstructions. Despite being purely geometric quantities, these calculations face significant challenges such as:
\begin{inparaenum}[\it (i)]
    \item Efficient computation of integrals for view factors, especially when considering specular surfaces that require multiple ray bounces.
    \item Managing large-scale mesh computations and data storage, particularly when detailed urban environments are modeled.
\end{inparaenum}

@@

In \cref{fig:solar-masks-vf}, we illustrate several aspects of solar masks: \textit{(i)} the solar masks of a building face oriented eastward, showing a discretization of the sun's position in \cref{fig:sm-building-east}; \textit{(ii)} the solar masks for an entire building, representing a detailed discretization of the sun's position throughout the day in \cref{fig:sm-whole-building}; \textit{(iii)} a visualization of the solar mask in the early morning for the city center of Strasbourg in \cref{fig:sm-strasbourg}; and \textit{(iv)} an image of a standard benchmark~\cite{van_eck_surface_2016} used for the computation of view factors and solving heat transfer problems between three building blocks in 2D in \cref{fig:view-factor}.

The grayscale values in each solar mask represent varying levels of solar obstruction for different azimuth and altitude angles.
In these masks, the scale ranges from 0 to 1, where 0 (white) indicates no obstruction and full exposure to sunlight, and 1 (black) represents full obstruction, meaning no sunlight reaches that part of the building face for the given sun position. 
Intermediate shades of gray indicate partial obstruction, where a portion of sunlight is blocked by surrounding buildings or other urban features.
The level of detail in the solar mask depends on the chosen level of discretization (LOD), as illustrated in \cref{fig:sm-building-east} and \cref{fig:sm-whole-building}.

%In \cref{fig:sm-building-east} (LOD-0), we see a coarser discretization with larger, generalized angular segments, leading to more abrupt transitions between obstructed and non-obstructed areas. In contrast, \cref{fig:sm-whole-building} (LOD-1) provides a finer level of detail, capturing more granular variations in solar accessibility across different sun angles. These masks help quantify the solar exposure of building surfaces over time, which is critical for accurately modeling heat gains and understanding the thermal dynamics of urban environments.

@@

\paragraph{Modelica for Multizone Heat Transfer}
Modelica offers extensive capabilities for multizone building energy simulations, utilizing models that range from simple (LOD-0) to more complex (LOD-1) representations. The multizone approach in Modelica is beneficial for modular and scalable simulations, where each building zone can be modeled with different fidelity based on the simulation requirements. This method leverages the generation of Functional Mock-up Units (FMUs), which integrate seamlessly into larger C/C++ applications, providing a robust framework for handling complex simulations involving multiple interacting systems.
The FMUs built from \cref{sec:heat-transfer-in-buildings} are loaded by the \texttt{Feel++} environment.
Input data for the models are sourced from available building information, such as geometric dimensions and material properties.
When specific data are unavailable, default values are assigned based on the building's construction year, referencing standard building codes or typical practices from that period.
Occupancy schedules are given as input to the models using reglementary occupancy.
We are currently working on parametrized occupancy profiles, which are adjusted based on the building's use type (e.g., residential, office, commercial).
This approach ensures that the models can be applied to a wide range of buildings, even when detailed information is limited.

@@

\subsubsection{Input data}

To run a KUB simulation, several input files need to be generated.
We have several metadata files (in JSON format), mesh data files (in MSH format), and meteorological measurement files (in CSV format).
\Cref{tab:input-data-size-comparison} lists these files with their corresponding sizes for New York City, see~\cref{fig:city-ny-largescale}, and a duration of one year for the simulation.
In addition, we compared the size of the input data with the size of the zone.

\begin{table}[ht]
  \centering
  \caption{Size comparison of input data files for different geographical extents in New York City}
  \label{tab:input-data-size-comparison}
  \begin{tabularx}{.8\linewidth}{l *{3}{>{\RaggedLeft\arraybackslash}X}} 
      \toprule
      \textbf{Files} & \textbf{\text{4 $\times$ 4} \si{\kilo\meter\squared}} & \textbf{\text{10 $\times$ 10} \si{\kilo\meter\squared}} & \textbf{\text{20 $\times$ 20} \si{\kilo\meter\squared}} \\
      \midrule
      \texttt{geographicdata\_setup.json} & \SI{4.0}{\kilo\byte} & \SI{4.0}{\kilo\byte} & \SI{4.0}{\kilo\byte} \\ 
      \texttt{gis.json} & \SI{23}{\mega\byte} & \SI{117}{\mega\byte} & \SI{470}{\mega\byte} \\
      \texttt{mesh\_lod0.msh} & \SI{17}{\mega\byte} & \SI{112}{\mega\byte} & \SI{496}{\mega\byte} \\
      \texttt{mesh\_lod1.msh} & \SI{44}{\mega\byte} & \SI{240}{\mega\byte} & \SI{896}{\mega\byte} \\
      \texttt{weather-data-0.hourly-variables.csv} & \SI{384}{\kilo\byte} & \SI{384}{\kilo\byte} & \SI{384}{\kilo\byte} \\
      \texttt{weather-data.json} & \SI{4.0}{\kilo\byte} & \SI{4.0}{\kilo\byte} & \SI{4.0}{\kilo\byte} \\
      \bottomrule
  \end{tabularx}
  \end{table}

In the future, the input data is expected to grow even larger with the addition of new details such as roofs, building characteristics, vegetation (e.g., trees), and terrain information.
These enhancements will increase the complexity and accuracy of the simulation and the amount of data required to accurately model the urban environment.

@@

The Urban Building pilot utilizes the Feel++ framework, supported by a robust CI/CD framework that facilitates efficient development and deployment.
A critical component for both Feel++ and KUB is the use of containerized environments, which encapsulate all necessary dependencies and configurations.

%This section outlines how GitHub Actions and Docker streamline the entire process, ensuring the robustness and productivity of the software development lifecycle.

>>>>

\documentclass[runningheads]{llncs}
\usepackage{fullpage}
\usepackage{graphicx} % for including images
\usepackage{float}
\usepackage[T1]{fontenc}
\usepackage{wrapfig}
\usepackage[]{subcaption}

\usepackage{url}
\usepackage{tikz}
\usepackage{xcolor}
\definecolor{darkred}{rgb}{0.6, 0, 0}
\definecolor{darkgreen}{rgb}{0, 0.5, 0}
\definecolor{darkblue}{rgb}{0, 0, 0.5}
\definecolor{darkmagenta}{rgb}{0.5, 0, 0.5}
\usepackage{hyperref}

@@

Building on the foundations of the Feel++ framework, this paper introduces an innovative CI/CD environment specifically designed for deployment on EuroHPC JU supercomputers. This environment enhances our ability to develop and test simulations rapidly and provides a robust platform for deploying and running these simulations at multiple scales. Integrating EuroHPC JU infrastructures represents a significant advancement in making high-performance computing resources accessible for urban simulation studies.

Thanks to synergies with other CoE HiDALGO2 pilots, the KUB project is set to integrate building simulations with Urban Air Pollution (UAP) pilot models to comprehensively assess the environmental impact of building stocks soon. This integration improves the predictive accuracy of the simulations by incorporating real-time data such as wind speed and solar radiation, enhancing the models' responsiveness and forecasts to environmental conditions.

@@

We describe our definition of Levels of Detail for Buildings such as:
\begin{itemize}
    \item \textbf{LOD-0:} The most straightforward form, representing buildings as oriented bounding boxes. This level is typically used for large-scale preliminary analyses and quick visual assessments.
    \item \textbf{LOD-1:} Buildings are represented as polygonal extrusions, with added roof structures to improve the visual accuracy and utility in simulations that do not require detailed internal features.
    \item \textbf{LOD-2:} At this level, buildings are detailed using Industry Foundation Classes (IFC) standards, supporting detailed thermal and structural analyses. This includes detailed geometries for each building entity, often using complex surface models like B-REP, swept solids, or CSG techniques.
\end{itemize}

\begin{figure}[ht]%{R}{1\textwidth} % 'R' or 'L' for right or left, and width
\centering
\subfloat[LOD-0: a building is represented by its bounding box]{%
  \includegraphics[width=0.48\linewidth]{img-compressed-buildings-lod0.png}
  \label{fig:building-lod0}
}
%\hfill % This ensures that the images are placed side by side
\subfloat[LOD-1: a building is represented by its ground footprint elevated to its height]{%
  \includegraphics[width=0.48\linewidth]{img-compressed-buildings-lod1.png}
  \label{fig:building-lod1}
}\\ % Ends the line for the first row of figures

\subfloat[LOD-2: a building in full detail using BIM. Note that LOD-2 and LOD-1 are mixed.]{%
  \includegraphics[width=0.48\linewidth]{img-compressed-buildings-lod2.png}
  \label{fig:building-lod2}
}
%\hfill
\subfloat[LOD-2: A zoom on the LOD-2 building.]{%
  \includegraphics[width=0.48\linewidth]{img-compressed-buildings-lod2-zoom.png}
  \label{fig:building-lod2-zoom}
}

\caption{Different representations of a building using our LOD definition}
\label{fig:buildings}
\end{figure}

In the figure~\ref{fig:buildings}, we illustrate the different levels of details. Panel~\ref{fig:building-lod0} displays the LOD-0 of a building with its bounding box. Panel~\ref{fig:building-lod1} displays the LOD-1 of a building using its footprint elevated to its height. Panel~\ref{fig:building-lod2} and~\ref{fig:building-lod2-zoom} display the LOD-2 representation using BIM. In the figure~\ref{fig:city-strasbourg}, we display an illustration of the center of the city of Strasbourg with LOD-0, see panel~\ref{fig:city-strasbourg-lod0}, and LOD-1, see panel~\ref{fig:city-strasbourg-lod1}, representations.

@@

\subsubsection{Terrain Modeling}
The terrain modeling process utilizes elevation data extracted from raster images. The initial step involves creating a uniform mesh based on the size of the raster image. Following this, the elevation at each node is evaluated.
However, this method provides a very refined mesh, even when the terrain is flat. For this reason, we plan to apply a mesh adaptation technique to reduce mesh density where feasible, using the following processing:
\begin{itemize}
    \item Compute an arbitrary number of isolines for elevation,
    \item Build a new terrain mesh conform with the isolines nodes and adapt to terrain elevation gradient.
\end{itemize}
%Subsequently, isolines for elevation are computed, and mesh adaptation techniques are applied to reduce mesh density where feasible. Finally, each tile is glued together to ensure the continuity of the terrain mesh.

\subsubsection{Vegetation Modeling}
Including vegetation (trees) in our geometric model is essential for the simulation of buildings. The shading provided by trees and the cooling provided by wooded areas had a significant impacts on building environment  . We use the OpenStreetMap database to obtain the metadata associated with the vegetation. In addition to the position of the trees, we can also obtain other information, such as the tree's height and species. The current strategy is as follows:
\begin{itemize}
\item Definition of a reference tree library that lists a certain number of tree species at different levels of precision (LOD). These geometric entities are parameterized so that a transformation can be applied.
\item Fetching vegetation metadata via OpenStreetMap. The attributes (height, species) are not always available, so we try to define them as best as we can (by searching around).
\item Creating a tree geometric model using an affine transformation of the reference tree model.
\end{itemize}

\subsubsection{Integration of all urban geometric components}
This process involves creating a conforming mesh that includes all components (buildings, terrains, vegetation). Moreover, this step requires accomplishing some challenges by using complex geometric algorithms to realize the following points: \textit{(i)} Ensure that buildings on slopes are accurately modeled by adapting their height and embedding them into the terrain mesh. The figure~\ref{fig:city-grenoble-terrain} illustrates this aspect; \textit{(ii)} applies the intersection of buildings and consequently defines contact zones that can be included in building thermal models (coupling). \textit{(iii)} Apply the intersection of vegetation with buildings and terrain; and finally \textit{(iv)} Improve mesh quality after the previous geometric operations (mesh adaption).

@@

Features using CGAL algorithms are not yet operational in our framework. We can reconstruct a geometric model of an urban area whose location is arbitrary so that the user can select an area anywhere in the world. The final mesh comprises all buildings in LOD-0 or LOD-1 and the terrain with elevation. The integration of all the urban components is currently being investigated. This part requires fairly costly algorithms (mesh intersection), for which it will be necessary to form groups intelligently to reduce the computational cost.

\paragraph{Current Mesh Generation Strategy}
The current strategy for mesh generation employs multi-threading (MT) to handle various stages of the mesh construction process. Initially, the used tiles are determined based on the specified location, a task performed sequentially. Following this, GIS data, including buildings and elevation information, is downloaded in parallel. Next, polygons are repaired~\cite{loriot_polygon_2024} to ensure they are suitable for mesh generation, with this process executed in parallel using MT. The terrain mesh is then generated in parallel, employing CGAL's algorithms to ensure precision and efficiency. Union operations at tile junctions are performed to ensure continuity, a step that is currently sequential. Finally, building meshes are generated using a parallel MT approach, leveraging CGAL for its advanced mesh generation capabilities.

@@

Data partitioning is a crucial stage in the deployment of the supercomputer simulator. We need to partition the geometry of the city in such a way as to distribute the simulation computation correctly.
Different partitioning strategies are considered depending on the specific requirements of the simulation use cases :
\begin{itemize}
\item Case 0: simple scenarios where buildings do not interact with their environment, a basic listing and weighting strategy is sufficient
\item Case 1: buildings interact with environmental elements, a more complex partitioning strategy is necessary that considers both the buildings and their immediate non-building surroundings. The build meshes and environment meshes (terrain, vegetation) are integrated conformably; each component can be partitioned separately.
\item  Case 2: for full interaction models, the partitioning strategy starts with the buildings and extends to the entire urban mesh, ensuring all elements are considered to minimize communication overhead.
\item Case 3: Regarding scenarios with extreme partitioning needs, Test Case 3 employs a multi-grid approach, defining coarse and fine meshes to manage computational resources efficiently. This multi-fidelity approach enhances the accuracy and applicability of urban models in simulations and ensures scalability across different computational platforms, making it a cornerstone of urban analysis.
\end{itemize}

The current version of our simulation framework has implemented case 0 and case 1. Cases 2 and 3 require a full conformal mesh, which is not yet available. Moreover, these partitioning strategies are costly, so we have planned to use other third-party tools, such as Zoltan2~\cite{the_zoltan2_team_zoltan2_nodate}, to improve efficiency.
\begin{wrapfigure}{R}{0.6\textwidth}
\centering
\subfloat[Partitioning Case 0\label{fig:city-strasbourg-lod0-parts}]{%
  \includegraphics[width=0.48\linewidth]{img-compressed-city-strasbourg-lod0-parts.png}
}
%\hfill % Ensures that the images are placed side by side
\subfloat[Partitioning Case 1\label{fig:city-strasbourg-lod1-parts}]{%
  \includegraphics[width=0.48\linewidth]{img-compressed-city-strasbourg-lod1-parts.png}
}
%\subfloat[Partitioning Case 3: Large scale\label{fig:city-ny-largescale}]{%
%  \includegraphics[width=0.4\textwidth]{img-compressed-city-newyork-largescale.png}
%}
\caption{Mesh partitioning illustrations}
\label{fig:partitioning}
\end{wrapfigure}

The figure~\ref{fig:partitioning} illustrates the different strategies discussed previously and presents a reconstruction of New York City in figure \ref{fig:city-ny-largescale}. This geometric model has an area of 400 $km^2$ (20 km square side of 20 km) and has generated around 450000 buildings. This example requires the large-scale approach discussed but not yet implemented or tested.

@@

@@

\paragraph{Numerical Methods and Challenges}
Both shading masks and view factors are computed using Monte Carlo and ray tracing techniques, which allow for handling complex geometries with various obstructions. Despite being purely geometric quantities, these calculations face significant challenges such as:
\begin{itemize}
    \item Efficient computation of integrals for view factors, especially when considering specular surfaces that require multiple ray bounces.
    \item Managing large-scale mesh computations and data storage, particularly when detailed urban environments are modeled.
\end{itemize}

@@

In the figure~\ref{fig:solar-masks-vf}, we illustrate \textit{(i)} the solar masks of building face oriented eastwise for a discretization of the sun position in the panel~\ref{fig:sm-building-east}, \textit{(ii)} the solar masks for an entire building for discretization of the sun position in the panel~\ref{fig:sm-whole-building}, \textit{(iii)} a visualization of the solar mask early morning of the city center of Strasbourg in panel~\ref{fig:sm-strasbourg} and \textit{(iv)} an image of a standard benchmark~\cite{van_eck_surface_2016} for the computation of view-factors and solving the heat transfer problems between three building blocks in 2D subsequently in panel~\ref{fig:view-factor}.

@@

\paragraph{Modelica for Multizone Heat Transfer}
Modelica offers extensive capabilities for multizone building energy simulations, utilizing models that range from simple (LOD-0) to more complex (LOD-1) representations. The multizone approach in Modelica is beneficial for modular and scalable simulations, where each building zone can be modeled with different fidelity based on the simulation requirements. This method leverages the generation of Functional Mock-up Units (FMUs), which integrate seamlessly into larger C/C++ applications, providing a robust framework for handling complex simulations involving multiple interacting systems.

@@

@@

The Urban Building pilot utilizes the Feel++ framework, supported by a robust CI/CD framework that facilitates efficient development and deployment. %This section outlines how GitHub Actions and Docker streamline the entire process, ensuring the robustness and productivity of the software development lifecycle.

\subsection{Standard CI/CD DevOps}
The development and deployment of KUB builds on top of the Feel++ CI/CD framework. It employs GitHub Actions and Docker: GitHub Actions automate real-time workflows to compile, test, and validate code changes, facilitating rapid development cycles and ensuring code quality. On the other hand, Docker provides a containerized environment that encapsulates Feel++ and its dependencies, ensuring consistent operations across diverse computing environments. These Docker images, customized for various system requirements, are maintained on the GitHub Container Registry (ghcr.io) to accommodate multiple deployment scenarios.
